\documentclass{standalone}

\begin{document}

\section{Introduction}

%Motivate and abstractly describe the problem you are addressing and how you are addressing it.
%What is the problem?
%Why is it important?
%What is your basic approach?
%A short discussion of how it fits into related work in the area is also desirable.
%Summarize the basic results and conclusions that you will present.

Machine learning is emerging in the insurance industry and is being applied
across multiple areas including the interpretation of data, business operations
and driver safety. One key application is claim prediction. Inaccuracies in car
insurance company's claim predictions raise the cost of insurance for good
drivers and reduce the price for bad ones. A more accurate prediction will
allow insurers to further tailor their prices, and hopefully make auto
insurance coverage more accessible to more drivers.

In this report, we based on Kaggle's Featured Prediction Competition
\emph{Porto Seguro's Safe Driver Prediction}\cite{kaggle}, conducted several
experiments, compared different approaches' effectiveness to tackle the claim
prediction problem, including \emph{logistic regression}, \emph{tensorflow
estimator} and \emph{random forest}.

The organization of the following report is as follows. In section II, we will
formally define the problem to solve and discuss the theoretical principle of
the algorithm we used. Then we will analyze the data feature and our method of
feature engineering in section III. After that, the experimental results are
shown and analyzed in section IV. Finally, we will discuss related works and
conclude the report.

\end{document}
